---
title: "p8105_hw1_yy3296"
author: "Yuze Yuan"
date: "2022-09-23"
output: github_document
---
## Problem 1
* import a package which includes drop_na function

```{r}
library(tidyverse) 
```

* Loading the package "palmerpenguins" which contains the dataset "penguins".
* Dropping all of NA form "penguins".

```{r}
data("penguins", package = "palmerpenguins")  
penguins_drop = drop_na(penguins) 
```
* Short description of the penguins dataset
  * This dataset has eight variables, which are species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, year. 
  * The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns. 
  * The mean flipper length is `r mean(penguins_drop$flipper_length_mm)`

* I make a scatterplot and save the scatterplot as a pdf.

```{r}
ggplot(penguins_drop,aes(x = bill_length_mm,y = flipper_length_mm,color=species)) + geom_point()
ggsave('scatterplot of problem1.pdf')
```

## Problem 2

* I Create a data frame composed of a random sample followed as normal distribution, a logical vector, a character vector, and a factor vector. 
```{r}
problem2_sample = tibble(
  norm_samp = rnorm(10),
  norm_samp_logical = norm_samp > 0,
  vec_char = c("hello", "my", "name", "is", "Yuze", "nice", "to", "meet", "you", "!"),
  vec_factor = factor(c("high", "high", "high", "high", "medium", "medium", "low", "low", "low", "low")),
)
```

* I take the mean of each variable of the data frame.

```{r}
mean_samp_norm = mean(pull(problem2_sample, norm_samp))
mean_samp_logical = mean(pull(problem2_sample, norm_samp_logical))
mean_vec_char = mean(pull(problem2_sample, vec_char))
mean_vec_factor = mean(pull(problem2_sample, vec_factor))
mean_samp_norm
mean_samp_logical
mean_vec_char
mean_vec_factor
```

* By taking the mean of each variable, we can see the random sample followed as normal distribution and the logical vector can work, but the character vector and the factor vector cannot work. 

* I convert the logical vector, character vector, and factor vector to numeric type. 

```{r}
num_samp_logical = as.numeric(pull(problem2_sample, norm_samp_logical))
num_vec_char = as.numeric(pull(problem2_sample, vec_char))
num_vec_factor = as.numeric(pull(problem2_sample, vec_factor))
```

* I found logical vector and factor vector can be converted to numeric type, but character vector cannot be converted to numeric type. Since the character vector composed of "words", it cannot be converted to numeric type. I think it helps explain what happens when I try to take the mean. For the character vector, since it composed of "words", it cannot work when calculating the mean. For the factor vector, althogh it can be converted to numeric type, the number is meaningless since each factor is parallel relationship instead of increasing or decreasing relationship, so the mean of the factor vector is meaningless. 
