---
title: "p8105_hw1_yy3296"
author: "Yuze Yuan"
date: "2022-09-23"
output: github_document
---
## Problem 1
* import a package which includes drop_na function

```{r}
library(tidyverse) 
```

* Loading the package "palmerpenguins" which contains the dataset "penguins".
* Dropping all of NA form "penguins".

```{r}
data("penguins", package = "palmerpenguins")  
penguins_drop = drop_na(penguins) 
```
* Short description of the penguins dataset
  * This dataset has eight variables, which are species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, year. 
  * The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns. 
  * The mean flipper length is `r mean(penguins_drop$flipper_length_mm)`

* I make a scatterplot and save the scatterplot as a pdf.

```{r}
ggplot(penguins_drop,aes(x = bill_length_mm,y = flipper_length_mm,color=species)) + geom_point()
ggsave('scatterplot of problem1.pdf')
```

## Problem 2

* I Create a data frame composed of a random sample followed as normal distribution, a logical vector, a character vector, and a factor vector. 
```{r}
problem2_sample = tibble(
  norm_samp = rnorm(10),
  norm_samp_logical = norm_samp > 0,
  vec_char = c("hello", "my", "name", "is", "Yuze", "nice", "to", "meet", "you", "!"),
  vec_factor = factor(c("high", "high", "high", "high", "medium", "medium", "low", "low", "low", "low")),
)
```

* I Take the mean of each variable of the data frame.

```{r}
mean_samp_norm = mean(pull(problem2_sample, norm_samp))
mean_samp_logical = mean(pull(problem2_sample, norm_samp_logical))
mean_vec_char = mean(pull(problem2_sample, vec_char))
mean_vec_factor = mean(pull(problem2_sample, vec_factor))
mean_samp_norm
mean_samp_logical
mean_vec_char
mean_vec_factor
```

* By taking the mean of each variable, we can see the random sample followed as normal distribution and the logical vector can work, but the character vector and the factor vector cannot work. 

