---
title: "p8105_hw1_yy3296"
author: "Yuze Yuan"
date: "2022-09-23"
output: github_document
---
## Problem 1
* import a package which includes drop_na function

```{r}
library(tidyverse) 
```

* load the package "palmerpenguins" which contains the dataset "penguins"
* drop all of NA form "penguins"

```{r}
data("penguins", package = "palmerpenguins")  
penguins_drop = drop_na(penguins) 
```
* short description of the penguins dataset
  * This dataset has eight variables, which are species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, year. 
  * The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns. 
  * the mean flipper length is `r mean(penguins_drop$flipper_length_mm)`

* make a scatterplot and save the scatterplot as a pdf

```{r}
ggplot(penguins_drop,aes(x = bill_length_mm,y = flipper_length_mm,color=species)) + geom_point()
ggsave('scatterplot of problem1.pdf')
```

## Problem 2

* create a data frame composed of a random sample followed as normal distribution, a logical vector, a character vector, and a factor vector. 
```{r}
problem2_sample = tibble(
  norm_samp = rnorm(10),
  norm_samp_logical = norm_samp > 0,
  vec_char = c("hello", "my", "name", "is", "Yuze", "nice", "to", "meet", "you", "!"),
  vec_factor = factor(c("high", "high", "high", "high", "medium", "medium", "low", "low", "low", "low")),
)
```


